(With Extensions)The Two Dualities of Computation: Negative and Fractional Types

### 2012-06-01 rational_ext.tex
_

\usepackage{graphicx}
%%\usepackage{longtable}
\usepackage{comment}
\usepackage{amsmath}
%%\usepackage{mdwlist}
%%\usepackage{txfonts}
\usepackage{xspace}
%%\usepackage{amstext}
\usepackage{amssymb}
\usepackage{stmaryrd}
\usepackage{proof}
\usepackage{multicol}
\usepackage[nodayofweek]{datetime}
\usepackage{etex}
\usepackage[all, cmtip]{xy}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{multicol}
\newcommand\hmmax{0} % default 3
\newcommand\bmmax{0} % default 4
\usepackage{bm}
\usepackage{cmll}

@@

@@

>>>>

\usepackage{graphicx}
%%\usepackage{longtable}
\usepackage{comment}
\usepackage{amsmath}
%%\usepackage{mdwlist}
%%\usepackage{txfonts}
\usepackage{xspace}
%%\usepackage{amstext}
\usepackage{amssymb}
\usepackage{stmaryrd}
\usepackage{proof}
\usepackage{multicol}
\usepackage[nodayofweek]{datetime}
\usepackage{etex}
\usepackage[all, cmtip]{xy}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{multicol}
\newcommand\hmmax{0} % default \newcommand\bmmax{0} % default 4
\usepackage{bm}
\usepackage{cmll}

@@

\begin{proposition}[Strong Normalizing]
\label{prop:termination-pi} 
{{langRev}} computation always terminate.

{{forall. c:b1<->b2, v:b1, exists v':b2.}}  
{{<c,v,[]> |-->  [c,v',[]]}}
\end{proposition}

@@

\roshan{We need to prove this. I am not sure how to start.}
\begin{proposition}[Strong Normalizing]
\label{prop:termination-piee-plus} 
Computations in {{langRev}} extended with {{eta+}} and {{eps+}} are
always terminating.
\end{proposition}

\roshan{This is straightforward.}
\begin{proposition}[Strong Normalizing]
\label{prop:termination-piee-times} 
Computations in {{langRev}} extended with {{eta*}} and {{eps*}} are
always terminating.
\end{proposition}

\roshan{We can present our construction here.}

\begin{proposition}[Strong Normalizing]
\label{prop:termination-piee} 
Computations in full {{langRevEE}} are weak normalizing.
\end{proposition}

\subsection{Logical Reversibility}

\begin{proposition}[Logical Reversibility]
{{langRev}} with {{eta+}} and {{eps+}} is logically reversible.
\end{proposition}
\roshan{Proof follows from compilation to {{langRevT}} }

\begin{proposition}[Logical Reversibility]
{{langRev}} with {{eta*}} and {{eps*}} is logically reversible.
\end{proposition}

This is an awkward one. I dont thnk that the above statement is
right.. At least not in the usualy sense. We can construct the
following combinators.

{{c1 : bool <-> bool}}

{{c1 true |--> {[true, false ]} }}

{{c1 false |--> {[true, false ]} }}

{{c1{dagger} true |--> {[true, false ]} }}

{{c1{dagger} false |--> {[true, false ]} }}

\noindent
And

{{c2 : bool <-> bool}}

{{c2 true |--> {[true, false ]} }}

{{c2 false |--> undefined }}

{{c2{dagger} true |--> true }}

{{c2{dagger} false |--> true }}

I don't think this issue will go away by any sort of choice of
top-level. I tried to design a top-level that can fix this -- I dont
think it is possible.
